### 2020-02-01 background.tex
local opt on sec 4
put in some refs

XXX.
Cite our stuff:
\cite{MM17_TR},
\cite{MM18_TR},
\cite{MM19_HTSR_ICML},
\cite{weightwatcher_package}
\cite{MM19_KDD},
\cite{MM20_SDM},
\cite{MM20_unpub_work}.
Cite also Ganguli review and maybe other stuff.
\charles{Gangulis work is not really close to what we are doing, although I get the politics.   The closest useful work would be the older work by Bouchaud and Potters, which discusses the statisical mechanics of heavy tailed and strongly correlated systems form the 90s}
\michael{Yes on both.}

@@

\paragraph{Norm-based capacity control theory.}
XXX.  MOST IRRELEVANT, BUT LIAO AND OUR SDM ARE RELATED.  
XXX.  MAYBE BEAT ON INFINITELY WIDE OR SOMETHING ELSE.

>>>>

Statistical mechanical ideas have long had influence on NN theory and practice~\cite{EB01_BOOK, MM17_TR, BKPx20}; and 
our best-performing metrics (i.e., those using fitted PL exponents and HT-SR Theory) are based on statistical mechanics ideas~\cite{MM17_TR, MM18_TR, MM19_HTSR_ICML, MM19_KDD, MM20_SDM}.
However, that the way in which we \emph{use} statistical mechanics theory is quite different than the way it is more commonly formulated.
Several very good overviews of the more common approach are available~\cite{EB01_BOOK, BKPx20}.
We will \emph{use} statistical mechanics theory more as it is used in quantitative finance.
Thus, much more relevant for our metholodogical approach is older work of Bouchaud, Potters, Sornette, and coworkers~\cite{BouchaudPotters03, SornetteBook, BP11, bun2017} on the statisical mechanics of heavy tailed and strongly correlated systems.

@@

\paragraph{Norm-based capacity control theory.}

There is also a large body of work on using norm-based metrics to bound generalization error~\cite{NTS15, BFT17_TR, LMBx18_TR}.
In this area, theoretical work aims to prove generalization bounds, and applied work uses these norms as a regularization function to improve training.
While we do find that norms provide relatively good quality metrics, at least for distinguishing good-better-best among well-trained models, we are not interested in proving generalization bounds or improving training.

### 2020-02-01 introduction.tex
local opt on sec 4
put in some refs

In more detail, our main contributions are the following.
\begin{itemize}
\item \michael{XXX TECHNICAL THING 1}
\item \michael{XXX TECHNICAL THING 2}
\item \michael{XXX TECHNICAL THING 3}
\item \michael{XXX TECHNICAL THING 4}
\end{itemize}

>>>>

In more detail, our main contributions are the following.
\begin{itemize}
\item \michael{XXX TECHNICAL THING 1}
\item \michael{XXX TECHNICAL THING 2}
\item \michael{XXX TECHNICAL THING 3}
\item \michael{XXX TECHNICAL THING 4}
\end{itemize}
MENTION: The most promising are metrics drawn from traditional statistical learning theory (e.g., norm-based capacity control metrics) as well as metrics (e.g., fitted power law metrics used to characterize the degree of strong correlations in a system) derived from the recently-developed Theory of Heavy-Tailed Self Regularization (HT-SR).
AND DEFINE HT-SR ACRONYM.
\michael{Sentence or two about how our metrics come from norm-based SLT and alpha-based HT-SR theory, since that is also highlighted in the abstract.}

SOMEWHERE CITE WEIGHTWATCHER: \cite{weightwatcher_package}
